Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-31 Grassmannian_cells.tex
Edited sections 3 and 4

Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view these as endofunctors acting on the category $\rep K(n)$. 
With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_2\Sigma_1$ and $\Sigma_1\Sigma_2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_1^2$.

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
  \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}

@@

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}
As $\Ext(P_m\otimes V,P_{m-1})=0$, we obtain a commutative diagram
\[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & 0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar^{ev_V}[u] & 0}.\]

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

@@

\begin{corollary}
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
\end{proof}

@@

In this section, we fix compatible bases for each $H_m=\Hom(P_{m-1},P_m)$ and use these to lift the (truncated) preprojectives to the universal cover of $K(n)$.
This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure.

@@

\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  The following holds:
  \begin{enumerate}
    \item For $m\geq 2$, we have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0;$$
    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \[\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\]
      On the universal covering, we have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  where $k\neq j_i$ for $i=1,\ldots,l$, $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$, $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first statement follows from Theorem \ref{covering}.
  For $m=1$, the second part is obvious.
  For $m\geq 2$, it then follows by applying the identities (\ref{recursive}).

  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence under consideration together with the first statement of this lemma.

  As $\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the second and third identity follows when applying $\Hom(\tilde P_{m},\underline{\quad})$.

  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$. Thus it follows that $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional. Thus we obtain the last identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$.
\end{proof} 
%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

@@

 We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
\begin{lemma}
  \label{le:subrep}
  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}
  Let $\uj\in I_l$.
  All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.	
\end{lemma}
\begin{proof}
Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.

@@

\newpage

\begin{lemma}
  \label{AR}
  \footnote{special case $m=3$}
  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.  Do parts (2), (3), (4) have analogues for $K(n)$?  The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.  The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}
  Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
  Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
  $$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$

  The following holds:
  \begin{enumerate}
    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$. What do we need? We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
    \item There exists a short exact sequences 
      \[\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\]
      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.
    \item We have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
    %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
  \end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$. Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively. We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section. Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.

@@

As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$
As $\Hom(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=0$ and $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ and $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$. Thus we can consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence obtained in course of the second statement. This yields the remaining results at once.\footnote{Lemma 5.2 and (3)-(5) zusammen}

>>>>

Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we can view these as endofunctors acting on the category $\rep K(n)$.

The endofunctors $\Sigma_1^2$ and $\Sigma_2^2$ are each naturally isomorphic to the identity maps on the full subcategories $\rep_{\langle 1\rangle} K(n),\rep_{\langle 2\rangle} K(n)\subset \rep K(n)$, where the objects of $\rep_{\langle i\rangle} K(n)$ are those representations of $K(n)$ which do not contain the simple $S_i$ as a direct summand.
Also, following \cite{brenner-butler}, the Auslander-Reiten translation $\tau:\rep K(n)\to\rep K(n)$ may be identified with the functor $\Sigma_2\Sigma_1$.

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark} \sayD{We need to change the conventions above to include notation for the equivalence between $\rep K(n)$ and $\rep K(n)^{op}$.}	\sayT{Changed it a bit}
  \label{rem:reflection recursion}
   \begin{enumerate}
	\item   These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
	\item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$ and $N$ is preinjective, then $\ses{(\Sigma_1\Sigma_2)^nM}{(\Sigma_1\Sigma_2)^nB}{(\Sigma_1\Sigma_2)^nN}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^nM}{\Sigma_2(\Sigma_1\Sigma_2)^nB}{\Sigma_2(\Sigma_1\Sigma_2)^nN}$ are short exact sequences without any preinjective direct summands. Without the assumption on the direct summands, it is not clear that short exact sequences are preserved. This is because $\Sigma_2 S_2=0$.
	\end{enumerate}

\end{remark}
 We will see that the indecomposable representations of dimension $\alpha(m,r):=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$ play an important role as they appear as quotients of morphisms between preprojective representations.
\begin{proposition}
  \label{pro:indecomposables}
  Let $m\geq 1$. Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
  The following hold:
  %\sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
    \item The set indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_\alpha(K(n))$. 
   % \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}

%For $m=1$, the action of $\Gl_n(\CC)$ on $\Gr_d(\CC^n)$ is transitive which shows that it is transitive on $\Ind_\alpha(K(n))$. As the reflection functors preserve indecomposability and isomorphism classes, by Lemma \ref{compatibleGSigma}, for every $g\in\Gl_n(\CC)$, we obtain a commutative diagram
%\[\xymatrix{\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}\ar[d]^{g^{-T}}&\Ind(K(n),\alpha(m+1,r))\ar[d]^g\\
%\Ind(K(n),\alpha(m,r))\ar[r]^{\Sigma_2}&\Ind(K(n),\alpha(m+1,r))}\]
%As the $\Gl_n(\CC)$-action is transitive on the left hand side, this implies that it is also transitive on the right hand side.
\end{proof}
\begin{remark}There is a more elegant way to prove Proposition \ref{pro:indecomposables} using the notion of stability and moduli spaces. Actually, fixing the standard stability induced by the linear form $\Theta(\alpha)=\alpha_2$, it can be shown that all indecomposables are stable and that the moduli space of stable representation is in fact $\Gr_d(\CC^n)$. We inserted this proof because the notion of stability were only used at this point and we wanted to keep this part as simple as possible. 
\end{remark}

@@

\begin{lemma}
  \label{le:injective evaluation maps}
Let $m\geq 1$.  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}\sayT{Maybe we can shorten the proof. I don't see a  proof which does not use reflection functors at the moment.}

As $\Ext(P_m\otimes V,P_{m-1})=0$ and $\Hom(P_1,I_1)=0$ respectively, we obtain a commutative diagram 
\[\xymatrix{0 \ar[r] & P_{m-1}\ar[r]^{\iota_{m-1}} & P_m\otimes H_m \ar[r]^{ev} &P_{m+1} \ar[r] & I_{2-m}\ar[r]&0\\0 \ar[r] & P_{m-1}\ar@{=}[u]\ar[r] &P_{m-1}\oplus P_m\otimes V \ar[r]\ar[u]^{(\iota_{m-1},\mathrm{id}_{P_m}\otimes \iota_V)} &P_{m}\otimes V \ar[r]\ar^{ev_V}[u] & 0}.\]
where $P_0=0$ and $I_{l}=0$ for $l\leq 0$. The snake lemma shows that $ev_V$ is injective if $m=1$ because $\mathrm{id}_{P_1}\otimes \iota_V$ is injective. In view of Remark \ref{rem:reflection recursion}, it is enough to show that the cokernel of $ev_V$ does not have a preinjective direct summand if $m=1$. Clearly the cokernel of $\mathrm{id}_{P_1}\otimes \iota_V$ is isomorphic to $P_1\otimes H_1/V$.

Thus we obtain the following commutative diagram induced by the cokernels of the above vertical maps where the vertical maps are surjective
\[\xymatrix{0\ar[r] & P_1\otimes H_1/V \ar[r] &K\ar[r]& I_{1}\ar[r]&0\\0 \ar[r]  & P_1\otimes H_1 \ar[u]\ar[r]^{ev} &P_{2}\ar[u] \ar[r] & I_{1}\ar@{=}[u]\ar[r]&0}\]
We need to show that $K$ has no preinjective direct summand. As $\Hom(P_2,P_1)=0$, the representation $K$ has no direct summand which is isomorphic to $P_1=S_1$. But this already shows that $K$ is indecomposable as $\udim K=(\dim H_1/V,1)$. Since $V$ is a proper subspace of $H_1$, $\udim K$ is not the dimension vector of a preinjective representation and the claim follows.

@@

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.\sayT{this is maybe not clear as we do not know that $P_{m+1}^V$ is indecomposable?! Therefore, I added a sentence.} Note that $\udim P_{m+1}^V <\udim P_{m+1}$, but $\udim P_r\geq \udim P_{m+1}$ if $\Hom(P_{m+1},P_r)\neq 0.$  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

@@

\begin{corollary}
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable. Moreover, every indecomposable of dimension $\udim P_{m+1}^V$ is truncated preprojective.
\end{corollary}
\begin{proof}
  By Lemma~\ref{le:unique morphisms}, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable. The second part follows from Proposition \ref{pro:indecomposables} together with Lemma \ref{le:unique morphisms}.
\end{proof}

@@

In this section, we fix compatible bases for each $H_m=\Hom(P_{m-1},P_m)$ and use these to lift the (truncated) preprojectives to the universal cover of $K(n)$.
This lifting will rigidify the situation and allow more precise control over these representations and their subrepresentation structure. A big advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering.

@@

\begin{lemma}\label{le:homdecomposition}\sayT{I split up some lemmas. Check references}
Let $m\geq 2$. The following holds:
\begin{enumerate}
\item We have $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional. 
\item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \begin{align}\label{ses1}\ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.\end{align}
  \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have $$\Hom(\tilde P_{m,i},\tilde P_{m,k})=\Ext(\tilde P_{m,i},\tilde P_{m,k})=0.$$

\end{enumerate}
\end{lemma}
\begin{proof}
The first part is a consequence of Theorem \ref{covering}. Now the observations of Section \ref{sec:truncated preprojectives} immediately yield the second part. The last part is also a consequence of Theorem \ref{covering} as, for $1\leq i\neq k\leq n$, we have 
$$\kk= \Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong \Hom_Q(P_{m},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})$$
which implies $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$. Now $\Ext(\tilde P_{m,i},\tilde P_{m,k})=0$ follows in the same manner using that $P_m$ is exceptional.

\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition. Note that, we can quotient out the lifted preproctives successively, i.e. we have short exact sequences
\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  Let $m\geq 2$ and let $\uj\in I_l$. The following holds:
  \begin{enumerate}
    \item 
    % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
    %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]

     We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\kk$  for $k\neq j_i$ for $i=1,\ldots,l$. 
		\item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\kk$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
		\item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.

  \end{enumerate}
\end{lemma} 
\begin{proof}

  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},\underline{\quad})$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.

The second identities are an immediate consequence of Lemma \ref{le:basic homological properties}, but can also be obtained when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).
%  As $\Hom(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m-1,j_i})=\Ext(\tilde P_{m},\tilde P_{m})=0$ and $\Hom(\tilde P_m,\tilde P_m)=\kk$, the identities in the second statement follow when applying $\Hom(\tilde P_{m},\underline{\quad})$ to (\ref{ses1}).

  For every $i=1,\ldots,l$, we have $\Hom(\tilde P_{m-1,j_i},\bigoplus_{i=1}^l \tilde P_{m-1,j_i})\cong\Hom(\tilde P_{m-1,j_i},\tilde P_m)=\kk$. Thus applying $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\underline{\quad})$ to (\ref{ses1}) yields $\Hom(\bigoplus_{i=1}^l \tilde P_{m-1,j_i},\tilde P^{\uj}_{m})=0$ because the representations $\tilde P_{m-1,j_i}$ are exceptional. In view of the second identity, we obtain the third identity when applying $\Hom(\underline{\quad},\tilde P^{\uj}_{m})$ to (\ref{ses1}).
\end{proof} 
%To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

@@

 We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
\begin{lemma}
  \label{le:subrep}
  \sayD{This should be moved to a statement on $K(n)$ and then deduced from that one.}\sayT{The proof seems to be more complicated in general because we cannot assume that $U'$ is indecomposable which means that it may have self-extensions. This is because $U\notin\tilde P_{m-1,l}^\perp$}
  Let $\uj\in I_l$.
  All non-trivial proper subrepresentations $U$ of $\tilde P_m^{\uj}$ are preprojective.	
\end{lemma}
\begin{proof}
Without loss of generality, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$ and denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ where $\tilde P_m^{(0)}=\tilde P_m$.

@@

\begin{lemma}
  \label{AR}
  \footnote{special case $m=3$}
  \sayD{Part (1) should follow from Corollary~\ref{cor:truncated preprojective isomorphism}.  Do parts (2), (3), (4) have analogues for $K(n)$?  The second half of (3) and part (5) should follow from Lemma~\ref{le:basic homological properties}.  The first half of (4) is roughly the same as Lemma~\ref{le:truncated extensions}.}\sayT{The sequence (6) should have an analogue on $K(n)$. I would be happy with a direct proof of (1) and (2). I did not check the details so far.
	(4) and the first half of (3) hold only on the universal cover. We should also have $\Ext(\tilde P_m^{\uj},P(m,\uj))\neq 0$ on $K(n)$.}
  Let $m\geq 4$ and $n-1\geq l\geq 1$, $\uj=(j_1,\ldots,j_l)\in I_l$ and $\uj':=(j_1,\ldots,j_{l-1})$.
  Consider the short exact sequence $$\sesm{\tilde P_{m-1,j_l}}{\tilde P_{m}^{\uj'}}{\tilde P_{m}^{\uj}}{\pi^{j_l}_{m,\uj'}}$$ and define
  $$P(m,\uj):=\bigoplus_{\substack{1\leq i\leq n\\i\neq j_l}}\tilde P_{m-2,(j_l,i)}\oplus \bigoplus_{i=1}^{l-1}\tilde P_{m-3,(j_l,j_l,i)}.$$

  The following holds:
  \begin{enumerate}
    \item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}=\tilde P_{m-2}^{(j_1,\ldots,j_l)}$.
    %\item We have $\tau\tilde P_{m}^{(j_1,\ldots,j_l)}\in ~^\perp(\tilde P_{m}^{(j_1,\ldots,j_l)})$.\footnote{not true for $m\geq 4$. What do we need? We have $\Hom(\tau\tilde P_{m}^{(j_1,\ldots,j_l)},\tilde P_{m}^{(j_1,\ldots,j_l)})=0$}
    \item There exists a short exact sequences 
      \begin{align}\label{ses3}\sesm{P(m,\uj)}{\tilde P_{m-1,j_l}}{\tau\tilde P_{m}^{\uj}}{\pi^{\bf j_l}_{m-1}}\end{align}
      where ${\bf j}_l=((1,\ldots,j_l-1,\widehat{j_l},j_{l}+1,\ldots,n),(j_1,\ldots,j_{l-1})).$
    \item We have $\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong \Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})=\kk$.

    %\item Finally, we have $\Ext(\tilde P_{m+1}^{(k-1)},V)=0$ for every subrepresentation $V$ of $\tilde P_{m-1}^{n-1}\oplus \tilde P_{m-2}^{n-k}$.
  \end{enumerate}%\footnote{introduce/consider/check indices, we have to mod out the corresponding reps in the covering} 
\end{lemma}
\begin{proof}
Using the identities (\ref{recursive}), it suffices to prove the all statements for $m=4$ and arbitrary $1\leq l\leq n-1$. Without loss of generality, we choose $(j_1,\ldots,j_l)=(1,\ldots,l)$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively. We should point out that it is very important for this prove that we consider fixed lifts of all representations in the universal covering as defined in the beginning of this section. Note that, starting with these cases, we only reflect at sources and no representation appearing is isomorphic to the simple injective representation $S_2$.

@@

As $\tilde P_m^{\uj}$ is exceptional on the universal covering by Lemma \ref{le:properties}, the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} imply 
$$\dim\Hom(\tilde P_{m}^{\uj},\tau \tilde P_{m}^{\uj})=\dim\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0 \text{ and } \dim\Ext(\tilde P_m^{\uj},\tau\tilde P_m^{j})=\dim\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=1.$$

We have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=0$ by Lemma \ref{le:basic homological properties}. As $\Ext(\tilde P_{4}^{\uj},\tilde P_{3,j_l})=\kk$ by a straightforward check, applying (\ref{recursive}), it follows that $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})=\kk$. This yields the third and forth identity.
